I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-06-21 paper_io_sim.tex
Minor fix

			For periodical flushing, our simulator searches in two page cache 
			LRU lists and flushes all the expired dirty data block. 
			A dirty data block is considered expired if the time from its last access 
			to current simulated time is longer than the predefined expire time. 
			Then the flushing time is calculated with total amount of flushed data.

@@

			The algorithm used to simulate file read is described in 
			Algorithm~\ref{alg:read}. 
			In Linux systems with write back storage devices, data can be either read 
			from cache with memory bandwidth or read from disk with disk bandwidth. 
			Therefore, total read time can be considered as a linear function 
			of the read time with each of these bandwidths, 
			enabling us to generalize reading process as two separate phases, 
			cache read and disk read. 
			In our simulator, when a user simulated application reads a file, 
			it sends a file read request to IOController. 
			First, dirty data is flushed to disk if needed to make the amount of 
			available memory enough to read the file.
			Data flushing function in MemoryManager is called, flushing time is 
			simulated and added to total run time (line 10).
			After data is flushed, MemoryManager is asked to evict data 
			from cache to accommodate the requested file (line 11). 
			Next, if file is cached either partially or entirely, MemoryManager is 
			called to re-access and update this cached data (line 13). 
			Then, periodical flushing is called to flushed expired dirty data 
			from cache (line 14).
			Since periodical flushing and cache read can be concurrent, the longer 
			time is added to simulated run time (line 15).
			If file is not cached or partially cached, a disk read is required (line 17). 
			Periodical flushing is called once again, but this time the flushing time is 
			added to total simulated time since flushing and disk read are time-shared, 
			or sequential in other words (line 18).
			Finally, data is read from disk to cache and managed by MemoryManager, 
			disk read time estimated by the storage model is added to 
			total simulated run time (line 19-20).

@@

			Algorithm~\ref{alg:write} describes our simulation of file write. 
			Initially, periodical flushing is called to flush expired dirty data 
			at the beginning of the write (line 10).
			Similar to the file read simulation, a file can also be written with 
			two different bandwidths, memory bandwidth and disk bandwidth. 
			Files can be written with memory bandwidth before the amount 
			of dirty data reaches dirty\_ratio. Thus, our algorithm initially checks 
			the amount of data that can be written with memory write 
			bandwidth (line 11-12).
			If this amount is greater than 0, MemoryManager is asked to evict 
			data from cache if needed and write this amount of data to cache 
			(line 14-15).
			The simulated run time can be added with the longer time of cache write 
			time and periodical flushing time because these can happen 
			concurrently (line 17).
			The amount of data that is not written with memory bandwidth is written 
			with disk bandwidth (line 18). 
			Now, the dirty ratio threshold is reached, we have to flush and evict 
			data from cache as much as possible so that 
			the remaining data can be written to cache (line 19-20). 
			Here, MemoryManager does not guarantee that the amount of flushed 
			and evicted data is enough for the remaining data. In the case it is 
			less than the required amount, the remaining data is written to cache 
			but then can be flushed and evicted right away. Thus, the amount 
			of remaining data that is written and kept in cache after the write 
			is limited by the amount free memory (line 21). 
			Finally, the write time is simulated, added to the total time and 
			returned to simulated applications (line 22).

>>>>

			For periodical flushing, our simulator searches in two page cache 
			LRU lists and flushes all the expired dirty data blocks. 
			A dirty data block is considered expired if the time from its last access 
			to current simulated time is longer than the predefined expire time. 
			The flushing time is calculated by storage simulation model with 
			total amount of flushed data.

@@

			The algorithm used to simulate file read is described in 
			Algorithm~\ref{alg:read}. 
			In Linux systems with write back storage devices, data can be either read 
			from cache with memory bandwidth or read from disk with disk bandwidth. 
			Therefore, total read time can be considered as a linear function 
			of the read time with each of these bandwidths, 
			enabling us to generalize reading process as two separate phases, 
			cache read and disk read. 
			When a user simulated application reads a file, 
			it sends a file read request to IOController. 
			First, dirty data is flushed to disk to make more available memory 
			to read the file if needed.
			Data flushing function in MemoryManager is called, flushing time is 
			simulated and added to total run time (line 10).
			After data is flushed, MemoryManager is asked to evict data 
			from cache to accommodate the requested file (line 11). 
			Next, if file is cached either partially or entirely, MemoryManager is 
			called to re-access and update this cached data (line 13). 
			Then, periodical flushing is called to flushed expired dirty data 
			from cache (line 14).
			Since periodical flushing and cache read can be concurrent, the time of 
			the longer activity between them is added to simulated run time (line 15). 
			If file is not cached or partially cached, a disk read is required (line 17). 
			Periodical flushing is called once again, but this time the flushing time is 
			added to total simulated time since flushing and disk read are time-shared, 
			or sequential in other words (line 18).
			Finally, data is read from disk to cache and managed by MemoryManager, 
			disk read time estimated by the storage model is added to 
			total simulated run time (line 19-20).

@@

			Algorithm~\ref{alg:write} describes our simulation of file write. 
			Initially, periodical flushing is called to flush expired dirty data 
			at the beginning of the write (line 10).
			Similar to the file read simulation, a file can also be written with 
			two different bandwidths, memory bandwidth and disk bandwidth. 
			Files can be written with memory bandwidth before the amount 
			of dirty data reaches dirty\_ratio. Thus, our algorithm initially checks 
			the amount of file data that can be written with memory write 
			bandwidth (line 11-12).
			If this amount is greater than 0, MemoryManager is asked to evict 
			data from cache if needed and to write this amount of data to cache 
			(line 14-15).
			The simulated run time can be added with the longer time of cache write 
			time and periodical flushing time because these can happen 
			concurrently (line 17).
			The amount of data that is not written with memory bandwidth is written 
			with disk bandwidth (line 18). 
			Now, the dirty ratio threshold is reached, we have to flush and evict 
			data from cache as much as possible so that 
			the remaining data can be written to cache (line 19-20). 
			Here, MemoryManager does not guarantee that the amount of flushed 
			and evicted data is enough for the remaining data. In the case it is 
			less than the required amount, the remaining data is written to cache 
			but then can be flushed and evicted right away. Thus, the amount 
			of remaining data that is written and kept in cache after the write 
			is limited by the amount free memory (line 21). 
			Finally, the write time is simulated, added to the total time and 
			returned to simulated applications (line 22).
